---
title: "Writing reports with R markdown"
author: "Tarrik Quneibi"
date: "2022-10-21"
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, warning=FALSE, message=FALSE, include=FALSE}
library('tidyverse')
library('here')
library('knitr')
library(kableExtra)
library(plotly)
```

This report was prepared for the UN . It analyzes the relationship between a countries GDP, life expectancy, and CO2 emissions. Our goal was to determine to what degree a country's economic strength or weakness may be related to it's public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions will increase with a county's GFP.

```{r data, include=FALSE}
gapminder_1997 <- read_csv(here("data\\gapminder_1997.csv"))


```


```{r gdp_lifeExp_1997, echo=FALSE}

p1 <- ggplot(gapminder_1997, aes(x=gdpPercap, y = lifeExp, size=pop/1000000, color=continent))+
  geom_point()+
  labs(x="GDP per capita", y="Life Expeectancy", title= "Do people in wealthy countries live longer?" ,
       size="Population (in millions)",
       color="Continent")

ggplotly(p1)
```


```{r tabular data}
n_countries <- gapminder_1997 %>%
  select(country) %>%
  n_distinct()
minGDP <- gapminder_1997 %>%
  summarize(min=min(gdpPercap)) %>%
  round(digits=2)
maxGDP <- gapminder_1997 %>%
  summarize(max=max(gdpPercap)) %>%
  round(digits=2)
```

The above plot shows the relationship between the GDP per capita and life expectany for a total of `r n_countries` countries. For this set of countries, economic wealth ranged from a minimum of $`r minGDP` to a maximum of $`r maxGDP` per capita.

| Summary of Data   |
|--------------------|-----------------|
|Number of countries | `r n_countries` |
|Minimum GDP per cap | `r minGDP`      |
|Maximum GDP per cap | `r maxGDP`      |

```{r tables}
gapminder_1997 %>%
  filter(continent == "Oceania") %>%
  kable()


```
## Using different syntax in RMarkdown

1. **R**
    + but python is a close second
2. *filter()*
3. ***Learn to visualize data more in depth***
4. [RMarkdown Reference Guide](chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf)


